%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Jaime Russo} \\ \vspace{1pt}
    \small (+351) 967 016 653 $|$ \href{mailto:itsjaimerusso@gmail.com}{\underline{itsjaimerusso@gmail.com}} $|$
    \href{https://www.linkedin.com/in/jaime-russo-13053422b/}{\underline{linkedin.com/in/jaime-russo}} $|$
    \href{https://github.com/jaimerusso}{\underline{github.com/jaimerusso}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {FCT NOVA -- Universidade Nova de Lisboa}{Caparica, Portugal}
      {MSc in Computer Science \& Engineering}{Sep. 2023 -- Nov. 2025}
    \resumeSubheading
      {FCT NOVA -- Universidade Nova de Lisboa}{Caparica, Portugal}
      {BSc in Computer Science \& Engineering}{Sep. 2020 -- Jun. 2023}
    \resumeSubheading
      {Magma Studio}{Online}
      {Magma Personal Finance MBA -- Financial Management Certification}{Issued Mar. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SAP Technical Analyst}{Oct. 2025 -- Present}
      {Stratesys Portugal}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{Responsible for technical analysis and systems integration within the SAP ERP ecosystem}
        \resumeItem{Develop and maintain integration flows using SAP CPI, Groovy, and ABAP}
      \resumeItemListEnd

    \resumeSubheading
      {Digital Marketing Engineer (Intern)}{Mar. 2025 -- Oct. 2025}
      {t\_insight}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{Applied software engineering principles to digital marketing by developing and maintaining platforms using PHP and WordPress}
        \resumeItem{Created automation tools to streamline marketing workflows and enhance technical implementation for data-driven campaigns}
      \resumeItemListEnd

    \resumeSubheading
      {MSc Thesis Developer -- AI \& RAG}{Sep. 2024 -- Nov. 2025}
      {t\_insight}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{Built \emph{t\_bot}, a Generative AI system for professional productivity using a dual-architecture approach (Backoffice RAG pipeline + Full-Stack App interface)}
        \resumeItem{Engineered a robust RAG pipeline with automated document ingestion, data grounding, and hallucination elimination}
        \resumeItem{Developed a scalable Full-Stack interface with real-time synchronization via WebSockets}
        \resumeItem{Implemented a contextual awareness layer for complex query understanding and precise retrieval}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{t\_bot} $|$ \emph{Python, LLMs, RAG, React, React Native, WebSockets, REST API}}{Sep. 2024 -- Nov. 2025}
          \resumeItemListStart
            \resumeItem{Developed an end-to-end Generative AI assistant for enterprise productivity in collaboration with t\_insight and FCT NOVA}
            \resumeItem{Designed a Backoffice RAG engine for automated document ingestion, grounding, and hallucination prevention}
            \resumeItem{Built a real-time Full-Stack interface using WebSockets for seamless user-AI interaction}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Scargraph} $|$ \emph{Computer Vision, AI, Business Strategy}}{Jan. 2024 -- Feb. 2024}
          \resumeItemListStart
            \resumeItem{Awarded 1st place out of 200+ proposals at the FCT NOVA 2024 Entrepreneurship competition, recognized by Asseco with the ``Inspired Technology'' Award}
            \resumeItem{Developed an innovative medical device leveraging Computer Vision and delivered a pitch with a full business model}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{3DShop} $|$ \emph{AI, Deep Learning, Software Development, Business Strategy}}{May 2024}
          \resumeItemListStart
            \resumeItem{Earned 3rd place in the Spring Hackathon organized by n.inf -- FCT NOVA, judged by Sky, Crossjoin Solutions, and Deloitte}
            \resumeItem{Ideated a Fashion E-commerce AI product, built an MVP, and delivered a pitch with competitor research and business model}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI \& Data}{: Large Language Models (LLMs), RAG, Conversational AI, Deep Learning, Azure AI} \\
     \textbf{SAP Ecosystem}{: SAP CPI, SAP ERP, Groovy, ABAP} \\
     \textbf{Languages}{: Python, Java, C, SQL, Kotlin, PHP, HTML/CSS} \\
     \textbf{Frameworks}{: React, React Native, Tailwind CSS, REST API, WebSockets, WordPress} \\
     \textbf{Developer Tools}{: Git, VS Code, Azure} \\
     \textbf{Engineering}{: Software Architecture, OOP, Concurrent \& Distributed Systems, Full-Stack Development, UX/UI} \\
     \textbf{Languages (Spoken)}{: Portuguese (Native), English (Advanced), Spanish (Advanced)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}